Precision calculations of the cosmic shear power spectrum projection

### 2017-02-03 limber2.tex
MK: Included Patrick's comments

The lensing potential $\psi$ in the Born approximation is defined as the
projected 3D metric potential $\Phi$ along the line of sight
\citep{1998ApJ...498...26K,BS01},
%
% Hu00 (21,22) with minus sign
%
\begin{equation}
  \psi(\theta, \varphi) = \frac 2 {{\rm c}^2} \int_0^{\chi_{\rm lim}} \frac{{\rm d}\chi}{\chi}
    \Phi[\chi, f_K(\chi) \theta, f_K(\chi) \varphi; \chi] \, q(\chi),
  \label{eq:psi}
\end{equation}
%
where the lensing efficiency $q$ is given by
%
\begin{equation}
  q(\chi) = \int\limits_\chi^{\chi_{\rm lim}} {\rm d} \chi^\prime \, n(\chi^\prime)
    \frac{f_K(\chi^\prime - \chi)}{f_K(\chi^\prime)},
  %
  \label{eq:lens_efficiency}
\end{equation}
%
corresponding to a population of lensed galaxies with source redshift
distribution $n(z) {\rm d}z = n(\chi) {\rm d} \chi$. Here, ${\rm c}$ is the
speed of light, the projection is carried out over comoving distances $\chi$ up
to a limiting distance $\chi_{\rm lim}$, and $f_K$ is the the comoving angular
distance, which depend on the spatial curvature of the Universe $K$.
%
This assumes a homogeneous galaxy distribution without clustering, so that the
redshift distribution in this approximation does not depend on the position
$(\theta, \varphi)$. Accounting for this position dependence leads to
correction of weak-lensing quantities due to clustering of source galaxies with
other sources \citep{2002A&A...389..729S}, and with galaxies associated with
lens structures \citep{1998A&A...338..375B,H02}.

@@

To specify tomographic redshift bins $i=0\ldots N_z-1$, we introduce a family
of lensing efficiency functions $q_i$ defined by a corresponding family of
redshift distributions $n_i$ via eq.~(\ref{eq:lens_efficiency}). The resulting
lensing potential is denoted by $\psi_{\ell m, i}$. The tomographic power
spectrum of the lensing potential between two redshift bins $i$ and $j$,
$C_{ij}^\psi$ is then defined by
%
\begin{equation}
  \left\langle \psi^{}_{\ell m, i} \, \psi^\ast_{\ell^\prime m^\prime, j} \right\rangle
    = \delta_{\ell \ell^\prime} \delta_{m m^\prime} C^\psi_{ij}(\ell) .
  \label{eq:C_ell_psi}
\end{equation}
%
Using the properties of the spherical harmonics (see
App.~\ref{sec:derivations_C} for details) the power spectrum can be written as
%
\begin{align}
  C_{ij}^\psi(\ell) = & \frac 8 {c^4 \pi} 
  \int_0^{\chi_{\rm lim}} \frac{{\rm d}\chi}{\chi} q_i(\chi)
  \int_0^{\chi^\prime_{\rm lim}} \frac{{\rm d}\chi^\prime}{\chi^\prime} q_j(\chi^\prime)
  \int {\rm d} k k^2 \, {\rm j}_\ell(k \chi) {\rm j}_\ell(k \chi^\prime) P_\Phi(k; \chi, \chi^\prime)
  \label{eq:C_ell_phi_Pphi} \\
  = & \frac 8 \pi \pref^2
  \int_0^{\chi_{\rm lim}} \frac{{\rm d}\chi}{\chi} \frac{q_i(\chi)}{a(\chi)}
  \int_0^{\chi^\prime_{\rm lim}} \frac{{\rm d}\chi^\prime}{\chi^\prime} \frac{q_j(\chi^\prime)}{a(\chi^\prime)}
  \int \frac{{\rm d} k}{k^2} \, {\rm j}_\ell(k \chi) {\rm j}_\ell(k \chi^\prime) P_{\rm m}(k; \chi, \chi^\prime) ;
  \label{eq:C_ell_phi_Pm}
\end{align}
%
where for convenience we defined the normalisation constant $\pref$ as
%
\begin{equation}
  \pref = \frac 3 2 \Omega_{\rm m} \left(\frac{H_0} c\right)^2.
  \label{eq:pref}
\end{equation}

@@

The tomographic shear power spectrum, in analogy to (\ref{eq:C_ell_phi_Pm}), is defined by
%
\begin{equation}
  \left\langle _2\gamma^{}_{\ell m, i} \; {}_2\gamma^\ast_{\ell^\prime m^\prime, j} \right\rangle
    = \delta_{\ell \ell^\prime} \delta_{m m^\prime} C^\gamma_{ij}(\ell).
  \label{eq:C_ell_gamma}
\end{equation}
%
For a flat Universe, this is given by
%
\begin{align}
  C^\gamma_{ij}(\ell) = \frac 1 4 \ellbar^2(\ell, 2) \, C^\psi_{ij}(\ell)
                 = & \frac 2 \pi \, \ellbar^2(\ell, 2) \, \pref^2
                 \int_{0}^{\chi_{\rm lim}} \frac{\rm d \chi}{\chi} \frac{q_i(\chi)}{a(\chi)}
                \int_{0}^{\chi_{\rm lim}} \frac{\rm d \chi^\prime}{\chi^\prime}
                \frac{q_j(\chi^\prime)}{a(\chi^\prime)}
                %\nonumber \\
                %& \times
                \int_0^\infty \frac{{\rm d} k}{k^2} \, P_{\rm m}(k, \chi, \chi^\prime) \,
                {\rm j}_\ell(k \chi) \, {\rm j}_\ell(k \chi^\prime) .
  \label{eq:C_ell_full}
\end{align}
%

@@

%
\begin{equation}
  \kappa(\theta, \varphi) = \frac 1 2 \edth \edth^\ast \psi(\theta, \varphi) = \frac 1 2 \nabla^2 \psi(\theta, \varphi).
  \label{eq:kappa_psi_spher}
\end{equation}
%
The spherical harmonics are eigenfunctions of the Laplacian,
%
\begin{equation}
  \nabla^2 {\rm Y}_{\ell m}(\theta, \varphi) = - \ell (\ell + 1) {\rm Y}_{\ell m}(\theta, \varphi)
    = - \ellbar^2(\ell, 1) {\rm Y}_{\ell m}(\theta, \varphi),
  \label{eq:nabla_Ylm}
\end{equation}
%
The potential power spectrum is then similar to the shear power spectrum
(\ref{eq:C_ell_gamma}) with a different spherical prefactor,
%
\begin{equation}
  C^\kappa_{ij}(\ell) = \frac 1 4 \ellbar^4(\ell, 1) \, C^\psi_{ij}(\ell)
    = \frac{\ell (\ell+1)}{(\ell-1)(\ell+2)} C^\gamma_{ij}(\ell) .
  \label{eq:C_ell_kappa_full}
\end{equation}
%
The convergence power spectrum is thus larger than the shear power spectrum, by
10\% for $\ell=4$, 1\% for $\ell = 14$, and less than 0.1\% for $\ell>45$.

@@

We follow \cite{2008PhRvD..78l3506L} who derive the second-order Limber
expansion for general projections from 3D to 2D scalar fields in the spherical,
all-sky case. First, we use the identity of Bessel functions
%
\begin{equation}
  {\rm j}_\ell(x) = \sqrt{\frac{\pi}{2x}} {\rm J}_{\ell + 1/2}(x)
\end{equation}
%
in eq.~(\ref{eq:C_ell_full}). Next, \cite{2008PhRvD..78l3506L} solve
integrals of the form
%
\begin{equation}
  \int_0^\infty {\rm d} \chi f(\chi) {\rm J}_{\ell + 1/2}(k \chi)
  = \int_0^\infty {\rm d} x k^{-1} f(x/k) {\rm J}_{\ell + 1/2}(x)
  \label{eq:int_dchi}
\end{equation}
%
by performing a Taylor expansion of the function $f$ around $x = k \chi = \nu$, where
the Bessel function has its approximate maximum. To separate the $k$- and
$\chi, \chi^\prime$-terms in (\ref{eq:C_ell_full}), we first approximate the
matter power cross-spectrum between two distances as geometric mean of the two
involved distances \cite{2016arXiv161200770K}, and divide out the growth factor
to define a redshift-independent power spectrum $P_{\rm m}(k)$,
%
\begin{equation}
 P_{\rm m}(k, \chi, \chi^\prime) = \sqrt{ P_{\rm m}(k, \chi) P_{\rm m}(k, \chi^\prime) },
    = D_+(\chi) D_+(\chi^\prime) P_{\rm m}(k).
  \label{eq:P_geom_mean}
\end{equation}
%
This is not exact, since some non-linear prescriptions of the power spectrum
depend on redshift other than the growth factor, for example when computing the
non-linear scale $k_{\rm NL}(z)$ for \texttt{halofit}.

@@

Following \cite{2008PhRvD..78l3506L} we expand to third order
%
\begin{equation}
  \lim_{\varepsilon \rightarrow 0} \int_0^\infty {\rm d} x \, {\rm e}^{-\epsilon (x - \nu)} g(x) {\rm J}_\nu(x) \approx g(\nu) - \frac 1 2 g^{\prime\prime}(\nu)
      - \frac \nu 6 g^{\prime\prime\prime}(\nu) 
\end{equation}
%
with $g(x) = k^{-1} f(\chi)$, $\chi=x/k$, and its derivatives $g^{(n)}(x) =
k^{-1-n} f^{(n)}(\chi)$. In our case the projection kernel is
%
\begin{equation}
  f(\chi) = D_+(\chi) a^{-1}(\chi) \chi^{-3/2} q(\chi).
  \label{eq:f_LA08}
\end{equation}
%
(Add indices $i, j$ to $f$ and $q$ for the tomographic case.)
%
Replacing both distance integrals in (\ref{eq:C_ell_full_Pk}) by their Taylor-expansions around $\nu = k \chi$ and $\nu = k \chi^\prime$,
respectively, yields
%
\begin{align}
  C^\gamma_{ij}(\ell) \approx & \, \ellbar^2(\ell, 2) \, \pref^2
    \int_0^\infty \frac{{\rm d} k}{k^3} \, P_{\rm m}(k) k^{-2}
    \left[ f_i(\chi) - \frac{1}{2 k^2} f_i^{\prime\prime}(\chi)
      - \frac{\nu}{6 k^3} f_i^{\prime\prime\prime}(\nu) + \ldots \right]
    %\nonumber \\
    %& \times
    \left[ f_j(\chi) - \frac{1}{2 k^2} f_j^{\prime\prime}(\chi)
    - \frac{\nu}{6 k^3} f_j^{\prime\prime\prime}(\nu) + \ldots \right]
  \label{eq:C_ell_limber2_dk}
\end{align}
%
Changing the integration to $\chi = \nu/k$ and collecting terms according to their $\nu$-dependence:
%
\begin{align}
  C^\gamma_{ij}(\ell) \approx & \, C^\gamma_{{\rm L1}, ij}(\ell) + C^\gamma_{{\rm L2}, ij}(\ell)
      \nonumber \\
    = & \frac{\ellbar^2(\ell, 2)}{\nu^4} \, \pref^2
    \int_0^\infty {\rm d} \chi \, \chi^3 \, P_{\rm m}\left( k \right)
    %\Bigg\{
    \left\{
    f_i(\chi) f_j(\chi)
    %\right.
      %\nonumber \\
    %&
    %\left.
     - \frac 1 {\nu^2} \left[ \frac{\chi^2}{2} \left( f^{}_i f^{\prime\prime}_j + f_i^{\prime\prime} f^{}_j \right)(\chi)
    + \frac{\chi^3}{6} \left( f^{}_i f^{\prime\prime\prime}_j + f^{\prime\prime\prime}_i f^{}_j \right)(\chi)
    \right]
    \right\}
    %\Bigg\}
  \label{eq:C_ell_limber12_dr}
\end{align}
%
The first term corresponds to the well-known first-order Limber approximation
\cite{1953ApJ...117..134L,1992ApJ...388..272K}, which is very widely used in
weak gravitational lensing. We retrieve the (spherical) standard expression by
inserting back the projection kernel (\ref{eq:f_LA08}) and the time-dependent
power spectrum,
%
\begin{align}
  C^\gamma_{{\rm L1}, ij}(\ell) = & \, \frac{\ellbar^2(\ell, 2)}{\nu^4} \, \pref^2 \int {\rm d} \chi \frac{ q_i(\chi) q_j(\chi) }{a^2(\chi)}
  P\left(k = \frac{\nu}{\chi}; \chi\right).
  \label{eq:C_ell_limber1}
\end{align}
%
In the Limber approximation, modes between structures at different epochs do
not contribute to the single line-of-sight integration.

@@

In Fig.~\ref{fig:Cl_cases} we plot the full shear power spectrum and some of
the approximations. For $\ell > 100$ all power spectra coincide to better than
one percent. The standard first-order Limber approximation is better than 10\%
but for the lowest $\ell$, but converges slowly to the true projection to
higher $\ell$. For the extended Limber approximations, despite slightly worse
for $\ell < 10$ in the hybrid cases, the errors with respect to the true power spectrum
decrease much faster, with $\ell^{-2}$.
Including the spherical prefactor decreases the difference by a
factor of a few for $\ell < 5$. Going to second-order yields percent accuracy
down to $\ell = 4$.

@@

  \caption{Shear power spectrum approximations compared in this paper. \mk{The last column will be removed in the
        final version.}}

  \begin{tabular}{|l|l|c|c|c|c}
  \hline
  Case & ID & eq.~ & $p(\ell)$ & $\nu(\ell)$ & Label [Comment paper] \\ \hline
  % 
  $1^{\rm st}$-order standard Limber, flat sky & L1Fl & (\ref{eq:P_ell_limber1}) + (i)
    & $1$ & $\ell$ & Kst \\ \hline
  %
  $1^{\rm st}$-order extended Limber, flat sky & ExtL1Fl & (\ref{eq:P_ell_limber1}) + (ii)
    & $\ell^4/(\ell+1/2)^4$ & $\ell + 1/2$ & ELF \\ \hline
  %
  $1^{\rm st}$-order extended Limber, hybrid, flat sky & ExtL1FlHyb & (\ref{eq:P_ell_limber1}) + (iii)
    & $1$ & $\ell + 1/2$ & ESt \\ \hline
  %
  $1^{\rm st}$-order extended Limber, spherical & ExtL1Sph & (\ref{eq:C_ell_limber1})
    & $\ellbar^2(\ell, 2)/(\ell+1/2)^4$ & $\ell+1/2$ & ELS \\ \hline
  %
  $2^{\rm st}$-order extended Limber, flat sky & Ext2FlHyb & (\ref{eq:P_ell_limber2}) + (iii)
    & $\ellbar^2(\ell, 2)/(\ell+1/2)^4$ & $\ell+1/2$ & - \\ \hline
  %
  $2^{\rm st}$-order extended Limber, spherical & Ext2Sph & (\ref{eq:C_ell_limber1})+(\ref{eq:C_ell_limber2_dr})
    & $\ellbar^2(\ell, 2)/(\ell+1/2)^4$ & $\ell+1/2$ & - \\ \hline
  %
  Full spherical & FullSph & (\ref{eq:C_ell_full}) &
      $\ellbar^2(\ell, 2)$ & - & - \\ \hline
  %
  \end{tabular}

@@

In Fig.~\ref{fig:xi_pm_K16} we show the correlation functions using the different cases
for the shear power spectrum. \mk{Replace this figure, don't show CFHTLenS data?}

@@

  \caption{Shear correlation funtions $\xi_+$ (\emph{left panels}) and $\xi_-$ (\emph{right}).
    The lower row shows the relative differences to the case Ext2Sph,  see Table \ref{tab:cases} for the different
    approximations and their symbols.
    %\cite{CFHTLenS-2pt-notomo}; the theotical predictions correspond to the best-fit parameters with
    %$\Omega_{\rm m} = 0.279$ and $\sigma_8 = 0.79$, except the red dashed curve with adapts a Planck-best fit
    %normalisation $\sigma_8 = 0.83$.
  }

>>>>

The lensing potential $\psi$ in the Born approximation is defined as the
projected 3D metric potential $\Phi$ along the line of sight
\citep{1998ApJ...498...26K,BS01},
%
% Hu00 (21,22) with minus sign
%
\begin{equation}
  \psi(\theta, \varphi) = \frac 2 {{\rm c}^2} \int_0^{\chi_{\rm lim}} \frac{{\rm d}\chi}{\chi}
    \Phi[\chi, f_K(\chi) \theta, f_K(\chi) \varphi; \chi] \, q(\chi),
  \label{eq:psi}
\end{equation}
%
where the lensing efficiency $q$ is given by
%
\begin{equation}
  q(\chi) = \int\limits_\chi^{\chi_{\rm lim}} {\rm d} \chi^\prime \, n(\chi^\prime)
    \frac{f_K(\chi^\prime - \chi)}{f_K(\chi^\prime)},
  %
  \label{eq:lens_efficiency}
\end{equation}
%
corresponding to a population of lensed galaxies with normalised source redshift
distribution $n(z) {\rm d}z = n(\chi) {\rm d} \chi$. Here, ${\rm c}$ is the
speed of light, the projection is carried out over comoving distances $\chi$ up
to a limiting distance $\chi_{\rm lim}$, and $f_K$ is the the comoving angular
distance, which depend on the spatial curvature of the Universe $K$.
%
This assumes a homogeneous galaxy distribution without clustering, so that the
redshift distribution in this approximation does not depend on the position
$(\theta, \varphi)$. Accounting for this position dependence leads to
correction of weak-lensing quantities due to clustering of source galaxies with
other sources \citep{2002A&A...389..729S}, and with galaxies associated with
lens structures \citep{1998A&A...338..375B,H02}.

@@

To specify tomographic redshift bins $i=0\ldots N_z-1$, we introduce a family
of lensing efficiency functions $q_i$ defined by a corresponding family of
redshift distributions $n_i$ via eq.~(\ref{eq:lens_efficiency}). The resulting
lensing potential is denoted by $\psi_{\ell m, i}$. The tomographic power
spectrum of the lensing potential between two redshift bins $i$ and $j$,
$C_{ij}^\psi$ is then defined by \cite{pee80}
%
\begin{equation}
  \left\langle \psi^{}_{\ell m, i} \, \psi^\ast_{\ell^\prime m^\prime, j} \right\rangle
    = \delta_{\ell \ell^\prime} \delta_{m m^\prime} C^\psi_{ij}(\ell) .
  \label{eq:C_ell_psi}
\end{equation}
%
Using the properties of the spherical harmonics (see
App.~\ref{sec:derivations_C} for details) the power spectrum can be written as
%
\begin{align}
  C_{ij}^\psi(\ell) = & \frac 8 {c^4 \pi} 
  \int_0^{\chi_{\rm lim}} \frac{{\rm d}\chi}{\chi} q_i(\chi)
  \int_0^{\chi^\prime_{\rm lim}} \frac{{\rm d}\chi^\prime}{\chi^\prime} q_j(\chi^\prime)
  \int {\rm d} k k^2 \, {\rm j}_\ell(k \chi) {\rm j}_\ell(k \chi^\prime) P_\Phi(k; \chi, \chi^\prime)
  \label{eq:C_ell_phi_Pphi} \\
  = & \frac 8 \pi \pref^2
  \int_0^{\chi_{\rm lim}} \frac{{\rm d}\chi}{\chi} \frac{q_i(\chi)}{a(\chi)}
  \int_0^{\chi^\prime_{\rm lim}} \frac{{\rm d}\chi^\prime}{\chi^\prime} \frac{q_j(\chi^\prime)}{a(\chi^\prime)}
  \int \frac{{\rm d} k}{k^2} \, {\rm j}_\ell(k \chi) {\rm j}_\ell(k \chi^\prime) P_{\rm m}(k; \chi, \chi^\prime) ;
  \label{eq:C_ell_phi_Pm}
\end{align}
%
where for convenience we defined the normalisation constant $\pref$ as
%
\begin{equation}
  \pref = \frac 3 2 \Omega_{\rm m} \left(\frac{H_0} c\right)^2.
  \label{eq:pref}
\end{equation}
%
The first line expresses $C_{ij}^\psi$ in terms of the 3D potential power spectrum $P_\Phi$, defined as
%
\begin{align}
  \left\langle \hat \Phi(\vec k; \chi) \hat \Phi^\ast(\vec k^\prime; \chi^\prime) \right\rangle
    = & (2\pi)^3 \delta_{\rm D}(\vec k - \vec k^\prime) P_\Phi(k; \chi, \chi^\prime).
    %\nonumber \\
    %= & (2\pi)^3 \delta_{\rm D}(\vec k - \vec k^\prime) \pref^2 k^{-4} a^{-1}(\chi) a^{-1}(\chi^\prime)
      %P_{\rm m}(k; \chi, \chi^\prime).
  \label{eq:p_phi}
\end{align}
%
The second line uses the 3D matter density power spectrum $P_{\rm m}$, which is defined analogously as
%
\begin{align}
  \left\langle \hat \delta(\vec k; \chi) \hat \delta^\ast(\vec k^\prime; \chi^\prime) \right\rangle
    = & (2\pi)^3 \delta_{\rm D}(\vec k - \vec k^\prime) P_{\rm m}(k; \chi, \chi^\prime),
  \label{eq:p_m}
\end{align}
%
and is
related to $P_\Phi$ via the absolute square of the Poisson equation (\ref{eq:poisson}).

@@

The tomographic shear power spectrum, in analogy to (\ref{eq:C_ell_phi_Pm}), is defined by
%
\begin{equation}
  \left\langle _2\gamma^{}_{\ell m, i} \; {}_2\gamma^\ast_{\ell^\prime m^\prime, j} \right\rangle
    = \delta_{\ell \ell^\prime} \delta_{m m^\prime} C^\gamma_{ij}(\ell).
  \label{eq:C_ell_gamma}
\end{equation}
%
For a flat Universe, this is given by
%
\begin{align}
  C^\gamma_{ij}(\ell) = \frac 1 4 \ellbar^2(\ell, 2) \, C^\psi_{ij}(\ell)
                 = & \frac 2 \pi \, \ellbar^2(\ell, 2) \, \pref^2
                 \int_{0}^{\chi_{\rm lim}} \frac{\rm d \chi}{\chi} \frac{q_i(\chi)}{a(\chi)}
                \int_{0}^{\chi_{\rm lim}} \frac{\rm d \chi^\prime}{\chi^\prime}
                \frac{q_j(\chi^\prime)}{a(\chi^\prime)}
                %\nonumber \\
                %& \times
                \int_0^\infty \frac{{\rm d} k}{k^2} \, P_{\rm m}(k, \chi, \chi^\prime) \,
                {\rm j}_\ell(k \chi) \, {\rm j}_\ell(k \chi^\prime) .
  \label{eq:C_ell_full}
\end{align}
%
The spherical prefactor for the full projection power spectrum is $p(\ell) =
\ellbar^2(\ell, 2)$, which will be modified under flat-sky and Limber
approximations below.

@@

%
\begin{equation}
  \kappa(\theta, \varphi) = \frac 1 2 \edth \edth^\ast \psi(\theta, \varphi) = \frac 1 2 \nabla^2 \psi(\theta, \varphi).
  \label{eq:kappa_psi_spher}
\end{equation}
%
The spherical harmonics are eigenfunctions of the Laplacian,
%
\begin{equation}
  \nabla^2 {\rm Y}_{\ell m}(\theta, \varphi) = - \ell (\ell + 1) {\rm Y}_{\ell m}(\theta, \varphi)
    = - \ellbar^2(\ell, 1) {\rm Y}_{\ell m}(\theta, \varphi),
  \label{eq:nabla_Ylm}
\end{equation}
%
The convergence power spectrum is then similar to the shear power spectrum
(\ref{eq:C_ell_gamma}) with a different spherical prefactor,
%
\begin{equation}
  C^\kappa_{ij}(\ell) = \frac 1 4 \ellbar^4(\ell, 1) \, C^\psi_{ij}(\ell)
    = \frac{\ell (\ell+1)}{(\ell-1)(\ell+2)} C^\gamma_{ij}(\ell) .
  \label{eq:C_ell_kappa_full}
\end{equation}
%
The convergence power spectrum is thus larger than the shear power spectrum, by
10\% for $\ell=4$, 1\% for $\ell = 14$, and less than 0.1\% for $\ell>45$.

@@

We follow \cite{2008PhRvD..78l3506L} who derive the second-order Limber
expansion for general projections from 3D to 2D scalar fields in the spherical,
all-sky case. First, we use the identity of Bessel functions
%
\begin{equation}
  {\rm j}_\ell(x) = \sqrt{\frac{\pi}{2x}} {\rm J}_{\ell + 1/2}(x)
\end{equation}
%
in eq.~(\ref{eq:C_ell_full}). Next, \cite{2008PhRvD..78l3506L} solve
integrals of the form
%
\begin{equation}
  \int_0^\infty {\rm d} \chi f(\chi) {\rm J}_{\ell + 1/2}(k \chi)
  = \int_0^\infty {\rm d} x k^{-1} f(x/k) {\rm J}_{\ell + 1/2}(x)
  \label{eq:int_dchi}
\end{equation}
%
by performing a Taylor expansion of the function $f$ around $x = k \chi = \nu$, where
the Bessel function has its approximate maximum. To separate the $k$- and
$\chi, \chi^\prime$-terms in (\ref{eq:C_ell_full}), we first approximate the
matter power cross-spectrum between two distances as geometric mean of the two
involved distances \cite{2016arXiv161200770K}, and divide out the growth factor
to define a redshift-independent power spectrum $P_{\rm m}(k)$,
%
\begin{equation}
 P_{\rm m}(k, \chi, \chi^\prime) = \sqrt{ P_{\rm m}(k, \chi) P_{\rm m}(k, \chi^\prime) }
    =: D_+(\chi) D_+(\chi^\prime) P_{\rm m}(k).
  \label{eq:P_geom_mean}
\end{equation}
%
This is not exact, since some non-linear prescriptions of the power spectrum
depend on redshift other than the growth factor, for example when computing the
non-linear scale $k_{\rm NL}(z)$ for \texttt{halofit}.

@@

Following \cite{2008PhRvD..78l3506L} we expand to third order
%
\begin{equation}
  \lim_{\varepsilon \rightarrow 0} \int_0^\infty {\rm d} x \, {\rm e}^{-\epsilon (x - \nu)} g(x) {\rm J}_\nu(x)
  %\approx g(\nu) - \frac 1 2 g^{\prime\prime}(\nu) - \frac \nu 6 g^{\prime\prime\prime}(\nu) 
  \approx g(\nu) - \frac 1 2 \left.\frac{{\rm d}^2 g}{{\rm d} x^2}\right|_{x=\nu}
                 - \frac \nu 6 \left.\frac{{\rm d}^3 g}{{\rm d} x^3}\right|_(x=\nu) ,
\end{equation}
%
with $g(x) = k^{-1} f(\chi)$, $\chi=x/k$, and its derivatives $g^{(n)}(x) =
k^{-1-n} f^{(n)}(\chi)$. In our case the projection kernel is
%
\begin{equation}
  f(\chi) = D_+(\chi) a^{-1}(\chi) \chi^{-3/2} q(\chi).
  \label{eq:f_LA08}
\end{equation}
%
(Add indices $i, j$ to $f$ and $q$ for the tomographic case.)
%
Replacing both distance integrals in (\ref{eq:C_ell_full_Pk}) by their Taylor-expansions around $\nu = k \chi$ and $\nu = k \chi^\prime$,
respectively, yields
%
\begin{align}
  C^\gamma_{ij}(\ell) \approx & \, \ellbar^2(\ell, 2) \, \pref^2
    \int_0^\infty \frac{{\rm d} k}{k^3} \, P_{\rm m}(k) k^{-2}
    \left[ f_i(\chi) - \frac{1}{2 k^2} f_i^{\prime\prime}(\chi)
      - \frac{\nu}{6 k^3} f_i^{\prime\prime\prime}(\chi) + \ldots \right]
    %\nonumber \\
    %& \times
    \left[ f_j(\chi) - \frac{1}{2 k^2} f_j^{\prime\prime}(\chi)
    - \frac{\nu}{6 k^3} f_j^{\prime\prime\prime}(\chi) + \ldots \right]
  \label{eq:C_ell_limber2_dk}
\end{align}
%
Changing the integration to $\chi = \nu/k$ and collecting terms according to their $\nu$-dependence:
%
\begin{align}
  C^\gamma_{ij}(\ell) \approx & \, C^\gamma_{{\rm L1}, ij}(\ell) + C^\gamma_{{\rm L2}, ij}(\ell)
      \nonumber \\
    = & \frac{\ellbar^2(\ell, 2)}{\nu^4} \, \pref^2
    \int_0^\infty {\rm d} \chi \, \chi^3 \, P_{\rm m}\left( k \right)
    %\Bigg\{
    \left\{
    f_i(\chi) f_j(\chi)
    %\right.
      %\nonumber \\
    %&
    %\left.
     - \frac 1 {\nu^2} \left[ \frac{\chi^2}{2} \left( f^{}_i f^{\prime\prime}_j + f_i^{\prime\prime} f^{}_j \right)(\chi)
    + \frac{\chi^3}{6} \left( f^{}_i f^{\prime\prime\prime}_j + f^{\prime\prime\prime}_i f^{}_j \right)(\chi)
    \right]
    \right\}
    %\Bigg\}
  \label{eq:C_ell_limber12_dr}
\end{align}
%
The first term corresponds to the well-known first-order Limber approximation
\cite{1953ApJ...117..134L,1992ApJ...388..272K}, which is very widely used in
weak gravitational lensing. We retrieve the (spherical) standard expression by
inserting back the projection kernel (\ref{eq:f_LA08}) and the time-dependent
power spectrum,
%
\begin{align}
  C^\gamma_{{\rm L1}, ij}(\ell) = & \, \frac{\ellbar^2(\ell, 2)}{\nu^4} \, \pref^2 \int {\rm d} \chi \frac{ q_i(\chi) q_j(\chi) }{a^2(\chi)}
  P_{\rm m}\left(k = \frac{\nu}{\chi}; \chi\right).
  \label{eq:C_ell_limber1}
\end{align}
%
In the Limber approximation, modes between structures at different epochs do
not contribute to the single line-of-sight integration.

@@

In Fig.~\ref{fig:Cl_cases} we plot the full shear power spectrum and some of
the approximations. The redshift distribution corresponds to CFHTLenS
\cite{CFHTLenS-2pt-notomo}. \mk{NL power spectrum parameters.}
For $\ell > 100$ all power spectra coincide to
better than one percent. The standard first-order Limber approximation is
better than 10\% but for the lowest $\ell$, but converges slowly to the true
projection to higher $\ell$. For the extended Limber approximations, despite
slightly worse for $\ell < 10$ in the hybrid cases, the errors with respect to
the true power spectrum decrease much faster, with $\ell^{-2}$. Including the
spherical prefactor decreases the difference by a factor of a few for $\ell <
5$. Going to second-order yields percent accuracy down to $\ell = 4$.

@@

  \caption{Shear power spectrum approximations compared in this paper. 'ID' is the abbrevation used in the plots.
    The third column shows the power-spectrum prefactor $p(\ell)$.  \mk{The last column will be removed in the
        final version.}}

  \begin{tabular}{|l|l|c|c|c|c}
  \hline
  Case & ID & eq.~ & prefactor & $\nu(\ell)$ & Label [Comment paper] \\ \hline
  % 
  $1^{\rm st}$-order standard Limber, flat sky & L1Fl & (\ref{eq:P_ell_limber1}) + (i)
    & $1$ & $\ell$ & Kst \\ \hline
  %
  $1^{\rm st}$-order extended Limber, flat sky & ExtL1Fl & (\ref{eq:P_ell_limber1}) + (ii)
    & $\ell^4/(\ell+1/2)^4$ & $\ell + 1/2$ & ELF \\ \hline
  %
  $1^{\rm st}$-order extended Limber, hybrid, flat sky & ExtL1FlHyb & (\ref{eq:P_ell_limber1}) + (iii)
    & $1$ & $\ell + 1/2$ & ESt \\ \hline
  %
  $1^{\rm st}$-order extended Limber, spherical & ExtL1Sph & (\ref{eq:C_ell_limber1})
    & $\ellbar^2(\ell, 2)/(\ell+1/2)^4$ & $\ell+1/2$ & ELS \\ \hline
  %
  $2^{\rm st}$-order extended Limber, flat sky & Ext2FlHyb & (\ref{eq:P_ell_limber2}) + (iii)
    & $\ellbar^2(\ell, 2)/(\ell+1/2)^4$ & $\ell+1/2$ & - \\ \hline
  %
  $2^{\rm st}$-order extended Limber, spherical & Ext2Sph & (\ref{eq:C_ell_limber1})+(\ref{eq:C_ell_limber2_dr})
    & $\ellbar^2(\ell, 2)/(\ell+1/2)^4$ & $\ell+1/2$ & - \\ \hline
  %
  Full spherical & FullSph & (\ref{eq:C_ell_full}) &
      $\ellbar^2(\ell, 2)$ & - & - \\ \hline
  %
  \end{tabular}

@@

In Fig.~\ref{fig:xi_pm_K16} we show the correlation functions using the different cases
for the shear power spectrum. The redshift distribution and cosmological model are the same 
as in Fig.~\ref{fig:Cl_cases}.

@@

  \caption{Shear correlation funtions $\xi_+$ (\emph{left panels}) and $\xi_-$ (\emph{right}).
    The lower row shows the relative differences to the case Ext2Sph,  see Table \ref{tab:cases} for the different
    approximations and their symbols.
    \mk{Probably remove ExtL1Fl, ExtL2Fl, we already showed for $P_\kappa$ that they are worse than standard
    Limber.}
    %\cite{CFHTLenS-2pt-notomo}; the theoretical predictions correspond to the best-fit parameters with
    %$\Omega_{\rm m} = 0.279$ and $\sigma_8 = 0.79$, except the red dashed curve with adapts a Planck-best fit
    %normalisation $\sigma_8 = 0.83$.
  }
